We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-21 paper/paper.tex
full tables

\begin{table*}
\centering
\begin{tabular}{|p{3.0cm}|p{6cm}| p{4.5cm}| c|}\hline
Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
\text{\cite{2005A&A...431..517K}} & RMS height in MW's 11 classical
satellites & Monte Carlo from an spherical power law
radial distribution. & $<0.5$ \\
\text{\cite{2005MNRAS.363..146L}} & Triaxiality of MW's 11 classical
satellites & 6 high resolution DM only N-body simulations. & High\\
\text{\cite{2005ApJ...629..219Z}} & Triaxiality and disk height in
MW's 11 classical satellites & 3 high resolution DM only N-body
simulations. & 2 \\
\text{\cite{2006AJ....131.1405K}} & RMS height in M31's 15 brightest
satellites & Monte Carlo satellite distributions with a power law
radial distribution & $87-99$\\
\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in MW's
11-13 brightest satellites & Monte Carlo from a halo triaxiality distribution from LCDM
simulations & $<0.5$\\
\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in M31's
16 brightest satellites & Monte Carlo from an spherical power law radial
distribution & $17$\\
\text{\cite{2009MNRAS.399..550L}}& Triaxiality in MW 11 classical satellites & 436 halos from a
cosmological N-body simulation ($1.3\times 10^{8}$\Msun particle mass)
&  High \\
\text{\cite{2013ApJ...766..120C}}& RMS height in M31's 27 brightest
satellites & Monte Carlo randomized satellite distribution & High\\
\text{\cite{2013MNRAS.429..725S}}& $c/a$ ratio in MW's 12 brightest
satellites & 6 High resolution DM only N-body simulations ($\sim
10^3$\Msun particle mass resolution) of individual halos & Low \\
\hline
\end{tabular}
\caption{Probability results derived in previous publications.}
\end{table*}

>>>>

\begin{table*}
\centering
\begin{tabular}{|p{3.0cm}|p{6cm}| p{4.5cm}| c|}\hline
Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
\text{\cite{2006AJ....131.1405K}} & RMS height in M31's 15 brightest
satellites & Monte Carlo satellite distributions with a power law
radial distribution & $87-99$\\
\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in M31's
16 brightest satellites & Monte Carlo from an spherical power law radial
distribution & $17$\\
\text{\cite{2013ApJ...766..120C}}& RMS height in M31's 27 brightest
satellites & Monte Carlo randomized satellite distribution & High\\
This Work & Triaxiality and RMS height in M31's 11-15 brightest
satellites & 24 halos in cosmological N-body Dark Matter only simulation ($\sim
10^{6}$\Msun particle mass resolution)& 56 \\
This Work & Triaxiality and RMS height in M31's 11-15 brightest
satellites & 20 halos in cosmological N-body hydro simulation ($\sim
10^{6}$\Msun particle mass resolution)& 27 \\
This Work & Triaxiality and RMS height in M31's 11-15 brightest
satellites & 12 high resolution DM only N-body simulations ($\sim
10^{5}$\Msun particle mass resolution) of individual halos & 37 \\
\hline
\end{tabular}
\caption{Probability results derived in previous publications for the
  triaxiality and/or root mean squared (RMS) height of M31 satellites.
\label{table:M31}}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{|p{3.0cm}|p{6cm}| p{4.5cm}| c|}\hline
Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
\text{\cite{2005A&A...431..517K}} & RMS height in MW's 11 classical
satellites & Monte Carlo from an spherical power law
radial distribution. & $<0.5$ \\
\text{\cite{2005MNRAS.363..146L}} & Triaxiality of MW's 11 classical
satellites & 6 high resolution DM only N-body simulations ($\sim10^5$
\Msun\ particle mass resolution). & High\\ 
\text{\cite{2005ApJ...629..219Z}} & Triaxiality and disk height in 
MW's 11 classical satellites & 3 high resolution DM only N-body
simulations. ($\sim10^6$ \Msun\ particle mass resolution) & 2 \\
\text{\cite{2007MNRAS.374.1125M}} & Triaxiality and RMS height in MW's
11-13 brightest satellites & Monte Carlo from a halo triaxiality distribution from LCDM
simulations & $<0.5$\\
\text{\cite{2009MNRAS.399..550L}}& Triaxiality in MW 11 classical satellites & 436 halos from a
cosmological N-body simulation ($1.3\times 10^{8}$\Msun\ particle mass)
&  High \\
\text{\cite{2013MNRAS.429..725S}}& $c/a$ ratio in MW's 12 brightest
satellites & 6 High resolution DM only N-body simulations ($\sim
10^3$\Msun particle mass resolution) of individual halos & Low \\
This Work & Triaxiality and RMS height in M31's 11-15 brightest
satellites & 24 halos in cosmological N-body Dark Matter only simulation ($\sim
10^{6}$\Msun particle mass resolution)& 3\\
This Work & Triaxiality and RMS height in M31's 11-15 brightest
satellites & 20 halos in cosmological N-body hydro simulation ($\sim
10^{6}$\Msun particle mass resolution)& 0.6 \\
This Work & Triaxiality and RMS height in M31's 11-15 brightest
satellites & 12 high resolution DM only N-body simulations ($\sim
10^{5}$\Msun particle mass resolution) of individual halos & 0.2 \\
\hline
\end{tabular}
\caption{Same as Table \ref{table:M31} for the MW satellites.
\label{table:MW}}
\end{table*}
